### 2013-12-28 thesis/src/chapters/chapter-5-design.tex
Thesis: hld overview part 2

\subsubsection{Knowledge base}
Knowledge base is represented as a set of rules, policies shared across autonomous components.

>>>>

Enforcing actions on a managed component can be done using different methods, however, all of them requires an agent installed in a managed resource. Cloud-SAP does not enforce any specific technology, leaving low-level decision to an implementation.

\subsubsection{Knowledge base}
Knowledge base is represented as a set of rules, policies shared across autonomic components.

-- TODO przyklad z ibma
